`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-03-05 paper/paper.qmd
make sure to track figures

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags:
  - epidemiology
  - R
  - infectious disease
authors:
  - affiliation: 1
    name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
  - affiliation: 1,3
    name: Chitra Saraswati
    orcid: 0000-0002-8159-0414
  - affiliation: 1,3
    name: Aarathy Babu
    orcid: 
  - affiliation: 4
    name: Michael Lydeamore
    orcid: 0000-0001-6515-827X
  - affiliation: 1,2
    name: Nick Golding
    orcid: 0000-0001-8916-5570
affiliations:
- index: 1
  name: The Kids Research Institute Australia, WA, Australia
- index: 2
  name:  University of Western Australia, WA, Australia
- index: 3
  name: Monash University, VIC, Australia
date: today
bibliography: paper.bib
---

>>>>

---
title: '`conmat`: generate synthetic contact matrices for a given age-stratified population'
format: 
  html: 
    keep-md: true
    fig-height: 4
    fig-align: center
    fig-format: png
    dpi: 300
tags:
  - epidemiology
  - R
  - infectious disease
authors:
  - affiliation: 1
    name: Nicholas Tierney
    orcid: 0000-0003-1460-8722
  - affiliation: 1
    name: Chitra Saraswati
    orcid: 0000-0002-8159-0414
  - affiliation: 1,3
    name: Aarathy Babu
    orcid: 
  - affiliation: 1
    name: Michael Lydeamore
    orcid: 0000-0001-6515-827X
  - affiliation: 1,2
    name: Nick Golding
    orcid: 0000-0001-8916-5570
affiliations:
- index: 1
  name: The Kids Research Institute Australia, WA, Australia
- index: 2
  name:  University of Western Australia, WA, Australia
- index: 3
  name: Monash University, VIC, Australia
date: today
bibliography: paper.bib
---
